Negative Selection in the 20th Century

### 2020-05-14 why-negative-selection.Rmd
trivia

---
title: "Negative Selection in the 20th Century"
author: "David Hugh-Jones, Abdel Abdellaoui"
date: "April 2020"
output: 
  bookdown::pdf_document2:
    toc: false
    latex_engine: xelatex
    keep_tex: true
---

>>>>

---
title: "Negative Selection in the 20th Century"
author: "David Hugh-Jones, Abdel Abdellaoui"
date: "April 2020"
output: 
  bookdown::pdf_document2:
    toc: false
    latex_engine: xelatex
---
